---
output: pdf_document
---
---
title: "homework presentation"
author: "AMEZOUWUI koffi"
date: "15 June,2020"
output: pdf_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# EXERCISE 1
## Variation in response explain 
```{r}
library(faraway)
data(teengamb)
head(teengamb)
model1=lm(gamble~sex+status+income+verbal,data = teengamb)
model1
summary(model1)
```
we have 52.67 percent of variation in response is explain by these predictors

```{r}
largest=model1$residuals
max(largest)
```
The largest (positive )residuals observation is 94.25222
### the case number
```{r}
match(max(largest),largest)
```
The case number is 24.

###c)the mean and median residuals
```{r}
moyenne=model1$residuals
mean(moyenne)
mediane=model1$residuals
median(mediane)
```
The mean of the residuals is -3.065293e-17 and the median is -1.451392
###d)correlation of residuals of fitted values
```{r}
cor(model1$residuals,model1$fitted.values)
```
The corelation of residuals and fitted values is -1.070659e-16

### EXERCISE 4
```{r}
data(prostate)
head(prostate)
summary(prostate)
model2=lm(lpsa~lcavol,data=prostate )
model2
x1=summary(model2)
x1
a1=x1$r.squared
a1
b1=x1$sigma
b1
model3=lm(lpsa~lcavol+lweight,data = prostate)
model3
x2=summary(model3)
a2=x2$r.squared
a2
b2=x2$sigma
b2
model4=lm(lpsa~lcavol+lweight+svi,data = prostate)
model4
x3=summary(model4)
a3=x3$r.squared
a3
b3=x3$sigma
b3
model5=lm(lpsa~lcavol+lweight+svi+lbph,data = prostate)
model5
x4=summary(model5)
a4=x4$r.squared
a4
b4=x4$sigma
b4
model6=lm(lpsa~lcavol+lweight+svi+lbph+age,data = prostate)
model6
x5=summary(model6)
a5=x5$r.squared
a5
b5=x5$sigma
b5
model7=lm(lpsa~lcavol+lweight+svi+lbph+age+lcp,data = prostate)
x6=summary(model7)
a6=x6$r.squared
a6
b6=x6$sigma
b6
model8=lm(lpsa~lcavol+lweight+svi+lbph+age+lcp+pgg45,data = prostate)
model8
x7=summary(model8)
a7=x7$r.squared
a7
b7=x7$sigma
b7
model9=lm(lpsa~lcavol+lweight+svi+lbph+age+lcp+pgg45+gleason,data = prostate)
model9
x8=summary(model9)
a8=x8$r.squared
a8
b8=x8$sigma
b8
```
I  Fit a model with lpsa as the response and l cavol as the predictor recording the residual standard error and the R2 
##creation du vecteur
```{r}
SIGMA=c(b1,b2,b3,b4,b5,b6,b7,b8)
RSQRT=c(a1,a2,a3,a4,a5,a6,a7,a8)
plotrange=c(1,2,3,4,5,6,7,8)
plot(plotrange,RSQRT,xlab ="Number of explanatory variables",ylab = "Residuals standard error" )
plot(plotrange,SIGMA,xlab ="Number of explanatory variables",ylab = "R squared" )

```
It is the trend of the two statistics

##EXERCISE 5
##Hints:  if x=ay+b,then y=(1/a)x-(b/a)   abline (y-intercept, slope )
##Nuage de points de lpsa et lcavol
```{r}
data(prostate)
attach(prostate)
plot(lpsa~lcavol,xlab="lcavol",ylab = "lpsa")
```
##The regressions
##If X=lcavol,y=lpsa
```{r}
fit1=lm(lpsa~lcavol,data = prostate)
fit2=lm(lcavol~lpsa,data = prostate)
plot(lcavol,lpsa)
abline(fit1$coeff[1],fit1$coeff[2],col="red")
abline(-fit2$coeff[1]/fit2$coeff[2],1/fit2$coeff[2],col="blue")
```
##therefore the two regression lines intersect at the point of averages
```{r}
mean(lcavol)
mean(lpsa)
```
##If x=lpsa,y=lcavol
```{r}
fit2=lm(lcavol~lpsa)
fit1=lm(lpsa~lcavol)
plot(lpsa,lcavol)
abline(fit2$coeff[1],fit2$coeff[2],col="red")
abline(-fit1$coeff[1]/fit1$coeff[2],1/fit1$coeff[2],col="blue")

```
             THE END 



J'ai maintenant je vais modifier le fichier voir...

Je fais deja une deuxième modification sur le fichier pour voir comment sa évolue.




